---
title: "HW576"
output: pdf_document
---

```{r}
##4
#a
X <- 1:100
lambdagen <- exp(1-0.04*X)
Y <-as.vector(rpois(X, lambda = lambdagen))
pdata <- as.data.frame(cbind(X, Y))
plot(X, Y)
```
```{r}
#b
X <- cbind(1, X)
beta <- matrix(rep(0, ncol(X)), nrow = ncol(X), ncol = 1) #initialize beta == 0
i <- 1 #counting iteration
maxi = nrow(X)
ones <- c(rep(1,100))
while(i <= maxi){
  eta <- X %*% beta
  mu <- exp(eta)
  V <- as.vector(mu)
  w <- diag(V)
  z <- eta + diag(ones/V)%*%(Y - mu)
  blast <- beta
  beta <- solve(t(X)%*%w%*%X)%*%t(X)%*%w%*%z
  if(abs(beta[2,] - blast[2,]) <= 1e-4)
    break
  i <- i + 1
}

fit <- glm(Y~X[,2], family = "poisson")
summary(fit)
#c
fisherin <- solve(t(X)%*%w%*%X)
fisherin
```
#b
The interation times is 5, which is also the result from the glm routine in R.
The beta from the iteration procedure is the following:
         [,1]
   0.95538073
X -0.03838775
which is also very close to the result from the glm routine in R

#c
the fisher information matrix is the following:
fisherin
                            X
   0.0354906454 -8.254298e-04
X -0.0008254298  3.388128e-05
```{r}
varb0b1 <- 0.0354906454 + 3.388128e-05 - 2*8.254298e-04
upper.list <- unlist(lapply(X, function(X) exp(0.95538073 - 0.03838775*X + qt(0.975, 98)*sqrt(varb0b1))))
lower.list <- unlist(lapply(X, function(X) exp(0.95538073 - 0.03838775*X - qt(0.975, 98)*sqrt(varb0b1))))
CI.matrix <- cbind(upper.list, lambdagen ,lower.list)
CI.matrix[101:200,] #I don't know why my matrix also includes the 100 intervals of x0
```
From the matrix above, we saw the 95% intervals includes the true value of lambda

```{r}
#d
datatotal <- cbind(X[,2], Y, lambdagen, mu)
plot(datatotal[,1], Y) 
points(datatotal[,1], lambdagen, col="red")
points(datatotal[,1], mu, col="blue")
```
The estimated values and the true means are very similar.
